### 2024-03-23 uw-ethesis-frontpgs.tex
new

Nested simulation procedures are commonly required for estimating tail risk measures for complex financial contracts or portfolios. 
In a standard nested simulation procedure, an outer simulation simulates $M$ risk scenarios under a real-world measure to reflect real-world uncertainties in portfolio values in different risk scenarios. 
For each outer scenario, inner simulation estimates the corresponding portfolio loss based on $N$ sample paths simulated under a risk-neutral measure according to  the risk-neutral pricing theory. 
This standard procedure is computationally expensive. 
For example, the simulation budget, i.e., the total number of inner sample paths in all outer scenarios, is a common way to measure the computation required for a simulation procedure. For the standard nested simulation procedure, the simulation budget is $\Gamma = MN$.
To alleviate computational burden of the standard procedure, many studies proposed to replace the inner simulation with alternative such as regression, kernel smoothing, likelihood ratio method, kernel ridge regression, etc. 
We refer to these alternatives as proxies. 
The above proxies have been demonstrated to have superior performance than the standard procedure in different examples.

The three parts of the thesis have different research focuses but serve one common theme.
Chapter 2 compares four existing nested simulation methods on their theoretical convergence properties and practical performance. 
Extensive numerical experiments are conducted for fair comparisons of proxy models on their practical performance in different angles. 
Proxies in chapter 2 fail to perform for high dimensional scenarios. 
In chapter 3, machine learning proxies are considered to model variable annuity contract losses.
Numerical experiments show that, for scenarios with temporal structure, time-series machine learning models are better proxies than generic machine learning models. 
The machine learning proxies are applied in a 2-stage nested simulation design. 
Experiments show that machine learning proxies outperform payoff-specific proxies.
Chapter 4 proposes direction for future research. In the 2-stage design, inner simulation in the second stage is still costly. 
We propose replacing stage 2 with machine learning proxy predictions. 
We test the accuracy, sensitivity, and resilience of such proposal.

>>>>

In the task of estimating risk measures for portfolios of complex financial derivatives, nested simulation procedures are commonly required but often computationally expensive. 
Tremendous efforts have been made to improve the efficiency of nested simulation procedures by approximating the inner simulation model with a proxy model. 
In this study, we review the literature on nested simulation procedures in financial engineering and establish fair comparisons of different proxy models using the same set of numerical examples. 
Our study shows interesting findings on the performance of different proxy models and provides useful insights for practitioners to choose proxy models for nested simulation procedures.
\cleardoublepage
